### 2023-01-26 README.Rmd
Point the Github repo to a less controversial site
Add bacl the missing tilde
Display the output of `graph` in README

``` r
remotes::install_github("GESIS-Methods-Hub/gran")
```

@@

```r
library(gran)
graph <- resolve(pkgs = c("openNLP", "LDAvis", "topicmodels", "quanteda"), snapshot_date = "2020-01-16")
graph
```

```{r, include = FALSE}
graph <- readRDS("tests/testdata/graph.RDS")
```

@@

```bash
cd rocker_test
sudo docker build -t gran .
sudo docker run --rm --name "grantest" -ti gran
```

>>>>

``` r
remotes::install_github("chainsawriot/gran")
```

@@

```r
library(gran)
graph <- resolve(pkgs = c("openNLP", "LDAvis", "topicmodels", "quanteda"), snapshot_date = "2020-01-16")
```

```{r, include = FALSE}
library(gran)
graph <- readRDS("tests/testdata/graph.RDS")
```

```{r example1}
graph
```

@@

```bash
cd ~/rocker_test
sudo docker build -t gran .
sudo docker run --rm --name "grantest" -ti gran
```
